### 2018-09-16 Sections/cryptowars.tex
all i need for the QKD hacking is now putting in the references

\subsection{Trojan horse attack}
The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by
sending light into their devices and collecting the reflected signal. 
The first one of this kind of attacks actually came for free for the eavesdropper\cite{}: it was discovered that some photon counters emits light when a photon was detected \cite{}. If the emitted light carries information on which detector was triggered, it must be prevented to leak out.

@@

A beam-splitting (BS) attack translates the fact that any signal lost in channel is stolen by Eve. Here Eve induces losses in the communication channel by putting a beam splitter outside Alice’s device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels and does not introduce any error.

@@

Eve can also go behond detector blinding. She can send in a powerful laser pulse to optically damage component in the QKD system and permanently change its characteristics\cite{}. If the new characteristics then assist the eavesdropper in an attack without Alice or Bob being notified, the security of that practical QKD system would be severly compromised.

A more detailed discussion on attacks on the physical implementation can be found in Ref.~\cite{}.

>>>>

\subsection{Trojan horse attack}
The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by
sending light into their devices and collecting the reflected signal. 
The first one of this kind of attacks actually came for free for the eavesdropper \cite{}: it was discovered that some photon counters emits light when a photon was detected \cite{}. If the emitted light carries information on which detector was triggered, it must be prevented to leak out.

@@

A beam-splitting (BS) attack translates the fact that any signal lost in channel is stolen by Eve. Here Eve induces losses in the communication channel by putting a beam splitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels and does not introduce any error.

@@

Eve can also go behond detector blinding. She can send in a powerful laser pulse to optically damage component in the QKD system and permanently change its characteristics\cite{}. If the new characteristics then assist the eavesdropper in an attack without Alice or Bob being notified, the security of that practical QKD system would be severly compromised.
% 
% 
A more detailed discussion on attacks on the physical implementation can be found in Ref.~\cite{}.
